\documentclass[mnsc]{informs3}
% [citeauthoryear]

\OneAndAHalfSpacedXI % current default line spacing
%%\OneAndAHalfSpacedXII
%%\DoubleSpacedXII
%%\DoubleSpacedXI

% If hyperref is used, dvi-to-ps driver of choice must be declared as
%   an additional option to the \documentstyle. For example
%\documentclass[dvips,mnsc]{informs3}      % if dvips is used
%\documentclass[dvipsone,mnsc]{informs3}   % if dvipsone is used, etc.

% Private macros here (check that there is no clash with the style)

% --------------------
\usepackage[utf8x]{inputenc}
% \usepackage[table]{xcolor}
% \usepackage{xcolor}
% \usepackage{listings}
% \usepackage{amsmath,amssymb}
% \usepackage[noend]{algpseudocode}
% \usepackage{stmaryrd}
% \usepackage{listings}
% \usepackage{algorithm}
% \usepackage{array}
% \usepackage{textcomp}
% \usepackage{pifont}
% \usepackage{bbding}
% \usepackage{comment}
% \usepackage{graphicx}

\usepackage{mathtools}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}

\usepackage{paper}
% \usepackage[svgpath=figures/]{svg}
% \usepackage[labelfont=bf]{caption}
% \captionsetup[table]{skip=5pt}

% \usepackage{academicons}
% \usepackage{cite}
% \usepackage[hidelinks,
% plainpages=false,
% pdftitle={
%   The Lead Time Syndrome
% },
% pdfauthor={Manuel Schneckenreither and Stefan Haeussler},
% pdfsubject={  The Lead Time Syndrome},
% pdfkeywords={production planning, order release, lead time syndrome, formalisation, detection,
%   operations research},
% ]{hyperref}

% \usepackage{url}


\newcommand\SH[2][r]{\ifx t#1 \textcolor{green!50!black}{[\textbf{SH:} #2]}
  \else \begin{center}\textcolor{green!50!black}{\textbf{SH:} #2} \end{center} \fi}

\newcommand\MS[2][r]{\ifx t#1 \textcolor{blue}{[\textbf{MS:} #2]}
  \else \begin{center}\textcolor{blue}{\textbf{MS:} #2} \end{center} \fi}

\newcolumntype{x}[1]{>{\centering\arraybackslash\hspace{0pt}}p{#1}}
% --------------------

% Natbib setup for author-year style
\usepackage{natbib}
 \bibpunct[, ]{(}{)}{,}{a}{}{,}%
 \def\bibfont{\small}%
 \def\bibsep{\smallskipamount}%
 \def\bibhang{24pt}%
 \def\newblock{\ }%
 \def\BIBand{and}%

%% Setup of theorem styles. Outcomment only one.
%% Preferred default is the first option.
\TheoremsNumberedThrough     % Preferred (Theorem 1, Lemma 1, Theorem 2)
%\TheoremsNumberedByChapter  % (Theorem 1.1, Lema 1.1, Theorem 1.2)
\ECRepeatTheorems

%% Setup of the equation numbering system. Outcomment only one.
%% Preferred default is the first option.
\EquationsNumberedThrough    % Default: (1), (2), ...
%\EquationsNumberedBySection % (1.1), (1.2), ...

% For new submissions, leave this number blank.
% For revisions, input the manuscript number assigned by the on-line
% system along with a suffix ".Rx" where x is the revision number.
\MANUSCRIPTNO{}

%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%

% Outcomment only when entries are known. Otherwise leave as is and
%   default values will be used.
%\setcounter{page}{1}
%\VOLUME{00}%
%\NO{0}%
%\MONTH{Xxxxx}% (month or a similar seasonal id)
%\YEAR{0000}% e.g., 2005
%\FIRSTPAGE{000}%
%\LASTPAGE{000}%
%\SHORTYEAR{00}% shortened year (two-digit)
%\ISSUE{0000} %
%\LONGFIRSTPAGE{0001} %
%\DOI{10.1287/xxxx.0000.0000}%

% Author's names for the running heads
% Sample depending on the number of authors;
% \RUNAUTHOR{Jones}
% \RUNAUTHOR{Jones and Wilson}
% \RUNAUTHOR{Jones, Miller, and Wilson}
% \RUNAUTHOR{Jones et al.} % for four or more authors
% Enter authors following the given pattern:
\RUNAUTHOR{Schneckenreither and Haeussler}
%\RUNAUTHOR{}

% Title or shortened title suitable for running heads. Sample:
% \RUNTITLE{Bundling Information Goods of Decreasing Value}
% Enter the (shortened) title:
\RUNTITLE{The Lead Time Syndrome}

% Full title. Sample:
% \TITLE{Bundling Information Goods of Decreasing Value}
% Enter the full title:
\TITLE{A Formalisation of the Lead Time Syndrome}

% Block of authors and their affiliations starts here:
% NOTE: Authors with same affiliation, if the order of authors allows,
%   should be entered in ONE field, separated by a comma.
%   \EMAIL field can be repeated if more than one author
\ARTICLEAUTHORS{%
  \AUTHOR{Manuel Schneckenreither%
    % \orcidID{0000-0002-4812-4665}
    % , Stefan Haeussler
    % \orcidID{0000-0003-2589-1367}
  }
  \AFF{Department of Information Systems, Production and Logistics Management, University of Innsbruck, Austria
    \EMAIL{manuel.schneckenreither@uibk.ac.at}
    \EMAIL{stefan.haeussler@uibk.ac.at}
  } %, \URL{}}

  % \AUTHOR{Stefan Haeussler % \orcidID{0000-0003-2589-1367}
  % }
  % \AFF{Department of Information Systems, Production and Logistics Management, University of Innsbruck, Austria
  % \EMAIL{stefan.haeussler@uibk.ac.at}}
} % end of the block

\ABSTRACT{%
  TODO
% Enter your abstract
}%

% Sample
%\KEYWORDS{deterministic inventory theory; infinite linear programming duality;
%  existence of optimal policies; semi-Markov decision process; cyclic schedule}

% Fill in data. If unknown, outcomment the field
\KEYWORDS{production planning, order release, lead time syndrome, formalisation, operations
  research}
\HISTORY{ % This paper was first submitted on April 12, 1922 and has been with the authors for 83 years
  % for 65 revisions.
}

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Samples of sectioning (and labeling) in MNSC
% NOTE: (1) \section and \subsection do NOT end with a period
%       (2) \subsubsection and lower need end punctuation
%       (3) capitalization is as shown (title style).
%
%\section{Introduction.}\label{intro} %%1.
%\subsection{Duality and the Classical EOQ Problem.}\label{class-EOQ} %% 1.1.
%\subsection{Outline.}\label{outline1} %% 1.2.
%\subsubsection{Cyclic Schedules for the General Deterministic SMDP.}
%  \label{cyclic-schedules} %% 1.2.1
%\section{Problem Description.}\label{problemdescription} %% 2.

% Text of your paper here

\section{Introduction}
\label{sec:introduction}

Introduce abbreviations:
\begin{itemize}
\item Lead Time Syndrome (\LTS{})
\item Work-in-process (\WIP{})\\
\end{itemize}


Definition LTS~\citep{selccuk2013adaptive}: dynamic quoting of lead times $\rightarrow$ lumpy releases $\rightarrow$ larger
WIP $\rightarrow$ longer lead times $\rightarrow$ more releases\\


Related literature \MS[t]{Cite!} argues that the lead time syndrome can only occur (i) if a lead
time is set dynamically and nonreciprocal according to the current \WIP{}-level and (ii) the order
releases monotonically depend on this lead time. In a practical point of view this assumption is
correct, however theoretically the interconnection between \WIP{}-level and number of releases is
not needed to infer this systematic releasing misbehavior. The dynamic quoting of the lead time can
rather be seen as origin and perpetuating factor for the \LTS{} in practical situations.

\begin{lemma}
  The interconnection between \WIP{}-level (and thus also the lead time for that sake), and the
  release pattern is not necessary to observe the systematic releasing misbehavior called lead time
  syndrome.
\end{lemma}

\begin{proof}{Proof}
  Consider a manufacturer with constant demand and an order release mechanism which strictly
  increases the number of orders to be released on every release decision, e.g.~by 1 order. Clearly
  the release decision does neither depend on the flow time nor the lead time. However, considered
  over time this leads to a monotonically increasing \WIP{}-level which again leads to a
  monotonically increasing lead time. This cycle of larger \WIP{}, longer lead time, and increasing
  amount of released orders is commonly known as lead time syndrome. \qed
\end{proof}

% \MS{name clash: LEAD TIME Syndrome with no LEAD TIME?}
Despite this theoretical observation the name lead time syndrome may be under question. However, as
in cases like the one given in the proof above the lead time follows the order release decisions and
in practice order releases are usually determined by the lead time (or flow time), the wording can
be considered as appropriate.
%
Nonetheless, our method is based on this observation. First we do not consider the lead time as
input variable to the method, then we do not suppose an interconnection between the \WIP{}-level
with the release decision procedure, and finally we do not restrict our method on any particular
order release pattern.


\section{The Lead Time Syndrome}
\label{sec:The_Lead_Time_Syndrome}

In this section we present a formalisation of the \LTS{}.
%
\MS[t]{TODO} The section is split into two
parts. First we will present the method for single-stage manufacturers, before considering more
stages.
%
It is straightforward to implement the presented methods to establish a \LTS{} detection system, see
Section~\ref{sec:Experimental_Evidence}. We follow the notation established
by~\cite{selccuk2013adaptive} to ease readability.

\subsection{Single-Stage Manufacturing System}
\label{subsec:Single-Stage_Manufacturing_System}


Consider a single product one-stage flow-shop manufacturing system that releases orders from the
order pool into the production system by an external mechanism.
%
Usually the orders are released based on the observed (average) flow time of the last finished
orders. However, our method does not presuppose such an interdependence for detecting the lead time
syndrome as it works directly on (parts of) the \WIP{}-level of the system. Thus our approach is
also able to observe systematic releasing misbehavior, referred to as \LTS{}, which do not consider
the lead time as depended variable for the release decisions.
%
% Intuitively the method works as
% follows. By measuring the change of the average \WIP{}-level over time and comparing this to the
% average releases into the system it can infer the desired property.
%
We denote the demand rate at time $t \geqslant 0$ as $\dr{t}$ \MS[t]{rates needed?}, and the demand
for the item during the period defined by timestamps $t_{2} \geqslant t_{1} \geqslant 0$ as
$\di{t_{1}}{t_{2}}$. Similarly we denote the order release rate as $\rr{t}$ and the releases within
a period as $\ri{t_{1}}{t_{2}}$. Each work-station $i$ is equipped with a queue $\q_{i}$ on which
released orders are appended according to a given routing and from there handed over to the
work-station if only if the work-station is empty and the order is at the head of the queue. Thus we
allow parallel processing of unique orders with non-shared queues in the setup. In case of shared
queues in this single item setup the work-station shall be considered as a single work-station. The
size of a queue $\size{\q_{i}} \geqslant 0$ is given by the number of orders within the queue.


\begin{definition}

  The \emph{queue size} $\size{\Q_{i}}$ of stage $i$ is defined as
  $\size{\Q_{i}} \defsym \sum_{i=1}^{n} \size{\q_{i}}$, where $n$ is the number of work-stations of stage
  $i$. Note that for this subsection $i=1$.

\end{definition}


As the demand may vary over time, e.g.~in a seasonal pattern or simply by some variance, it must be
considered as time factor in the formulation of the lead time syndrome. To clarify, consider a
seasonal demand. It can clearly not be considered a lead time syndrome if the releases just depict
the demand.

\MS{maybe use continuous representation below?}

\begin{definition}
  The \emph{periodised demand} $\dper{p}$ for any period $p \in \Nat$ is given by
  $\dper{p} = \max(0,\dmean(\frac{p+p+1}{2}) + \epsilon) = \di{p}{p+1}$, where $\dmean$ is a
  function which maps any given period to the expected mean demand at this period and $\epsilon$ is
  drawn from a random variable $\X$ with mean $0$ and standard deviation $\sigma$. Note that $f$
  must not necessarily be continuous.
  % Note that the periodised demand is only defined over natural numbers, which describe the current
  % period.
\end{definition}


\begin{example}
  In case of a constant demand, $\dmean$ maps to a constant value and $\epsilon = 0$, whereas for a
  seasonal demand $f$ in a continuous space one may use the sine-function and
  $\X \sim \N{0}{\sigma^{2}}$.
  %
  \MS[t]{maybe refer to inventory control, as there $\N{0}{\cdot}$ is also used?}

  % In most cases we expect the random variable to be drawn from the
  % standard distribution $\X \sim \N{0}{\sigma^{2}}$ and in case of a discrete demand space applying
  % the nearest integer function.
\end{example}

In practise the available demand data is used to infer the function $\dmean$ and the value for
$\sigma$. This is done using regression and other statistical analyses. Therefore, hereafter the
function $\dmean$ and the value for $\sigma$ % these values
are expected to be known. In the following we will use these values to infer important time
information for the analysis of the \LTS{}.

% \MS{needed at all? we got the variance. But the max operator is used?}
% \begin{definition}
%   We define the \emph{mean deviation demand} $\ddev{t}$ with time $t \geqslant 0$ as
%   $\ddev{t} \defsym \di{t}{t+1} - \dmean(\frac{2t+1}{2})$. That is we subtract the mean from the
%   demand to be able to investigate the deviations solely.
%   % \begin{align*}
%   %   \ddev{t} \defsym
%   %   \begin{cases}
%   %     1 + \epsilon & \text{iff }\dmean(\frac{2t+1}{2}) = 0\\
%   %     \dmean^{-1}(\frac{2t+1}{2}) \cdot \dmean(\frac{2t+1}{2}) + \epsilon & \text{otherwise}
%   %   \end{cases}
%   %   \tpkt
%   % \end{align*}
%   % Note that $\dmean(\cdot)$ is a scalar value and thus the inverse $\dmean^{-1}(\cdot)$ exists
%   % unless the mean demand is $0$.
% \end{definition}
% The standardised demand allows us to extract useful information from the deviations of the

\begin{lemma}


  % stddev(dem1) > stddev(dem0) -> stddev(rel1) > stddev(rel0)


  Let $p \in \Nat$ be the periods. Consider two demand streams where the deviations of the mean
  demand are drawn by $\X_{0}$, $\X_{1}$ and the corresponding release pattern follow the random
  variables $\Lambda_{0}$ and $\Lambda_{1}$ respectively.
  % and the standard deviation $\stddev$ over a set of discrete
  Then, if $\stddev(\X_{1}) > \stddev(\X_{0})$  then $\stddev(\Lambda_{1}) > \stddev(\Lambda_{0})$
  is sensible.
  %
  Informally this means that for higher standard deviation in the demand a higher standard deviation
  in the release pattern is sensible.

  % It is sensible to increase the standard deviation in the release pattern if the standard
  % deviation in the demand increases.


\end{lemma}

\begin{proof}{Proof by induction on the size of the deviations.}
  Wlog assume sufficient capacity for the single-stage manufacturer.
  % Base: stddev(dem1) > 0 -> stddev(rel1) > 0
  In case of a constant demand pattern, the only sensible release pattern is to release s.t. an over
  the time (nearly) constant output in the magnitude of the demand is achieved.
  % or the maximum achievable constant throughput.
  Any other release pattern will increase either back-orders or finished goods inventory and thus
  costs. Similarly the costs increase once variability in the demand is introduced, as possible
  unforeseen fluctuations in the demand require either to increase the stock level or accept
  back-order costs.
  %
  % IH: stddev(dem1) > stddev(dem0) -> stddev(rel1) > stddev(rel0)
  In case the demand deviation increases by any magnitude greater $0$, chances for the demand
  quantities further away from the mean are increased with probability $p>0$. Thus the planner has
  to decide whether to release additional quantity to be able to serve the demand which is more
  likely with probability $p$. Clearly, this increases chances for either inventory costs or
  back-order costs according to the decision of the planner and compared to the previous situation.
  \qed

  % Demand with higher stddev
  % ----
  % ---
  % --
  % ---
  % ----

  % Demand with lower stddev
  % ---
  % ---
  % ---
  % ---
  % ---


\end{proof}


% The above lemma thus specifies that for higher standard deviation in the demand higher fluctuations
% in the release pattern are sensible.
Thus, the deviations of the demand in relation to the mean specify a proportional % natural
lower-bound of release decisions to consider in the analysis of the \LTS{}.
%
Hence, we use the standard deviation $\sigma$ of the random variable $\X$ related to the mean demand
as measure for determining the time span of the release decisions and \WIP{}-levels being considered
in the analysis.
%
% Recall that the standard deviation measures the expected deviation of
% the mean in orders.
%
%
% Thus, $2 \sigma$ specify the (minimum) expected deviation of the demand and thus also the release
% decisions from one period to the next.
%


\MS{2 definitions. 1. How many periods to average using $\sigma$. 2. How many periods to look back
  for the time: season length. }

\begin{definition}
  We define the \emph{\mddname{}} $\mdd{p}$ of period $p$ and the manufacturing system
  % with the periodised demand $\dper{\cdot}$
  under investigation as
  \begin{align*}
    \mdd{p} \defsym 1 +
    \frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=1}^{p}{f(i)}}  +
    \frac{\max \{|f(i)-f(i+1)|\ \mid \ \forall 0 \leqslant i \leqslant p \}}{\frac{1}{p} \cdot \sum_{i=1}^{p}{f(i)}}
  \end{align*}
  \MS{maybe use moving average for mean. Imagine a demand jump from bottom to top and vice versa! should
    be equal? }
  where $\zs$ can be used to select the confidence interval of the underlying distribution. Thus
  under the assumption of a normal distribution and according to the $68$--$95$--$99.7$ rule,
  $68.3\%$, $95.5\%$, or $99.7\%$ of the demand deviation are used by setting $\zs$ to $1$, $2$, and
  $3$ respectively.
  % This
  % definition assumes a symmetric probability distribution of $\X$ in the second term. However,  due
  % to the ceiling function
  % For asymmetric
  % probability distributions, the definition can be easily extended to integrate
\end{definition}

\begin{definition}
  The \emph{\avgrqname} $\avgrq{p}$ of period $p$ is defined as
  \begin{align*}
    \avgrq{p} \defsym \frac{1}{K} \cdot \sum_{i=p-K}^{p-1}{ \ri{i}{i+1} }\tcom
  \end{align*}

  where $K=\min(p,\ceil{\mdd{p}})$.
\end{definition}

\MS{TODO: same for \WIP{}}


Intuitively the \mddname{} is a measure of variability and maximum leap of the mean in the demand
stream with respect to the average mean demand and equipped with a lower-bound of $1$. We use the
\mddname{} to average the number of releases and \WIP{}-levels to be able to investigate their
\textsl{\mddname{}}-average slopes.


% Maybe here an example?
We compare these slopes to the slopes from the past. The amount of time which is looked into the
past is defined by the defined by the length of the season.


Futhermore,... \MS[t]{seasonal stuff}
%


\begin{definition}
  We define the \emph{time span} $\ts{p}$ in period $p$ of the manufacturing system
  % with the periodised demand $\dper{\cdot}$
  under investigation as
  \begin{align*}
    \ts{p} \defsym 1 + % \ceil[\Bigg]{
    \frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=1}^{p}{f(i)}}
    % }
    +
    \MS[t]{\text{seasonal stuff}} \tcom
  \end{align*}
  where $\zs$ can be used to select the confidence interval of the underlying distribution. Thus
  under the assumption of a normal distribution and according to the $68$--$95$--$99.7$ rule,
  $68.3\%$, $95.5\%$, or $99.7\%$ of the demand deviation are used by setting $\zs$ to $1$, $2$, and
  $3$ respectively.
  % This
  % definition assumes a symmetric probability distribution of $\X$ in the second term. However,  due
  % to the ceiling function
  % For asymmetric
  % probability distributions, the definition can be easily extended to integrate
\end{definition}


To reduce the impact of outliers we average the actual releases over $\ts{p}$ values.


- je mehr variation im demand desto länger die zeit


Zumindest durschnittlich gleichbleibende Freigabemenge bei über die Zeit steigender EDT (oder
eventuell die Warteschlangenlänge [von Stage 1]).


\begin{definition}
  The \emph{Lead Time Syndrome} is defined as
\end{definition}

% *Informelle Definition LTS_+*


\subsection{Multi-Stage Manufacturing System}
\label{subsec:Multi-Stage_Manufacturing_System}


We now lift the established metric to multi-stage manufacturing systems.


\section{Experimental Evidence}
\label{sec:Experimental_Evidence}


\section{Conclusion}
\label{sec:Conclusion}


\bibliography{references}
\bibliographystyle{plainnat}

\end{document}

% --------------------
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
